# Life Expectancy Increases

To dramatically show the increases in life expectancy by country from 1960 to 2010, I plot the variable in 1960 versus itself in 2010.  The line of equivilance (a 45% angle) is used as a reference and shows the result that you would see if there where no growth.  The vertical distance from this line is the increase in life expectancy. I also superimpose a linear model on top of the scatter plot.  You can see that the gains are greater for countries that started off with lower life expectancies.    

```{r, echo = F}

# Public holiday data
data0 <- readxl::read_xlsx("raw_data/Life Expectancy at Birth.xlsx") %>%
  filter(!is.na(Region), Gender == "Total") %>%
  select(-Gender) %>%
  mutate(CountryName = countrycode::countrycode(`Country Name`, "country.name", "country.name"))

Variation <- data0 %>%
  group_by(`Country Name`) %>%
  summarise(sd = sd(`Life Expectancy`, na.rm = T)) %>%
  arrange(sd) %>%
  filter(!is.na(sd))

data <- data0 %>% inner_join(Variation)

compare <- inner_join(
  data0 %>% filter(Year == 1960) %>% 
    rename(`Life Expectancy 1960` = `Life Expectancy`) %>% 
    select(`Life Expectancy 1960`, `Country Code`),
  data0 %>% filter(Year == 2010) %>% rename(`Life Expectancy 2010` = `Life Expectancy`)
) %>%
  mutate(squared = `Life Expectancy 1960`^2) 


```


A random sample from the data set: 
```{r, echo = F}
knitr::kable(sample_n(compare, 5), format = "html")
```

---


```{r life_expect, eval = F, echo = F}
ggplot(compare) +
  aes(x = `Life Expectancy 1960`) + 
  aes(y = `Life Expectancy 2010`) +
  geom_point() +
  geom_smooth(se = F, method = "lm") +
  geom_abline(slope = 1, intercept = 0, lty = 2) +
  aes(xend = `Life Expectancy 1960`) +
  aes(yend = `Life Expectancy 1960`) +
  geom_segment(mapping = aes(col = "Gain from 1960 to 2010")) +
  geom_segment(mapping = aes(y = 0, col = "Country Expectancy in 1960")) +
  scale_color_manual( breaks = c("Gain from 1960 to 2010",  "Country Expectancy in 1960"), values = c("grey59", "grey30", "grey30")) +
  geom_point(aes(y = `Life Expectancy 1960`), col = "grey30") +
  geom_point() +
  labs(subtitle = "@EvaMaeRey | source: data.worldbank.org", size = .7) +
  labs(title = "Life Expectancy at Birth by Country") + 
  labs(col = "") +
  theme(legend.title = element_blank()) +
  theme_bw() +
  xlim(c(20, 80))
```


`r paste(knitr::knit(text = partial_knit_chunks("life_expect")), collapse = "\n")`


---
