# Dietary Restrictions

This vis challenge focused on communicated on the percentage in different regions of people that adheare to dietary restrictions of various types.  There are two categories that are displayed: geographic area and dietary restriction type.  I sorted both of these variables by greatest impact for graphing, so that the display would look more orderly and easier to digest; no pun intended.  

```{r, fig.width=12, echo = F}
data <- readxl::read_xlsx("raw_data/Restricted Dietary Requirements Around The Globe.xlsx")

DietRegionAverage <- data %>%
  group_by(Diet) %>%
  summarise(mean = mean(Followers)) %>%
  mutate(Region = "SimpleAverageAllRegions") %>%
  arrange(mean)

DietOrder <- DietRegionAverage$Diet

RegionDietAverage <- data %>%
  group_by(Region) %>%
  summarise(mean = mean(Followers)) %>%
  mutate(Diet = "SimpleAverageAllDiets") %>%
  arrange(mean)

RegionOrder <- RegionDietAverage$Region

data <- data %>% mutate(Diet = factor(Diet, levels = DietOrder), Region = factor(Region, levels = RegionOrder))
```


A random sample from the data set: 
```{r, echo = F}
knitr::kable(sample_n(data, 5))
```


```{r}
ggplot(data) +
  aes(x = Region, y = Diet, label = Followers * 100) +
  # geom_point() +
  geom_text() +
  geom_rect(aes(
    xmin = as.numeric(Region) + .25 - Followers * .5,
    xmax = as.numeric(Region) + .25,
    ymin = as.numeric(Diet) - .25,
    ymax = as.numeric(Diet) + .25
  ), fill = "red", alpha = .3) +
  geom_rect(aes(
    xmin = as.numeric(Region) - .25,
    xmax = as.numeric(Region) + .25 - Followers * .5,
    ymin = as.numeric(Diet) - .25,
    ymax = as.numeric(Diet) + .25
  ), fill = "green", alpha = .3) +
  # coord_equal() +
  labs(size = "Percentage\nFollowing") +
  theme_classic(base_size = 15) +
  labs(title = "Percent of Area Inhabitants with given Dietary Restriction")
```

```{r}

ggplot(data) +
  aes(Diet, Followers * 100) +
  geom_col() +
  facet_grid(Region ~ .) +
  ggtitle("Restricted Dietary Requirements Around The Globe",
    subtitle =
      "Neilsen Report, 2016: \"What's in Our Food and on Our Minds\""
  )
```

