# Public Holidays

The public holidays visualization task posed a challenge at the outset.  There were many types of holidays in the dataset, and it was unclear which were considered public holidays in the original visualization.

The idea of what Andrew Gelman terms "Garden Paths" came to mind -- i.e. how researcher choices may result in quite different analysis outcomes.  I produce several world maps based on different plausible researcher choices.  

```{r, echo = F}
# library(rgdal)

# Public holiday data
data0 <- readxl::read_xlsx("raw_data/Public Holidays around the world (final).xlsx") %>% 
  mutate(CountryName = countrycode::countrycode(Country, "country.name", "country.name"))
 
Countries = data0 %>% group_by(Country, CountryName) %>% summarise()
```

A random sample from the data set: 
```{r, echo = F}
knitr::kable(sample_n(data0, 5))
```

```{r}
# Mapping data
world_map_df = map_data("world") %>% 
  mutate(CountryName=countrycode::countrycode(region, "country.name", "country.name"))

CountriesWorldMap = world_map_df %>% group_by(CountryName, region) %>% summarise()
```

```{r}
# create a blank ggplot theme
theme_opts <- list(theme(panel.grid.minor = element_blank(),
                        panel.grid.major = element_blank(),
                        panel.background = element_blank(),
                        plot.background = element_rect(fill="#e6e8ed"),
                        panel.border = element_blank(),
                        axis.line = element_blank(),
                        axis.text = element_blank(),
                        axis.ticks = element_blank(),
                        axis.title = element_blank(),
                        plot.title = element_text(size=15)))

hitsList=c("Bank", "Public", "National", "Federal", "Official")

pickList=c()
for(i in 1:200){
pickList[i] =
  paste(sort(
    unique(c("Bank","Public",
             sample(hitsList,replace = T)))), 
    collapse = "|")
}
pickList=unique(c(pickList))[1:8]

for (i in pickList){


NumBankHolidays = data0 %>% 
  filter(stringr::str_detect(`Holiday Type`, i )) %>% 
  group_by(CountryName) %>% 
  summarise(count=n()) 
#Some values were not matched unambiguously: Micronesia, Saint Martin, St. Barts
table(NumBankHolidays$`Holiday Type`)


NumBankHolidays %>% group_by(CountryName) %>% summarise()

data=world_map_df %>% left_join(NumBankHolidays) %>% mutate(count=ifelse(is.na(count), 0, count))


# plot maps
print(ggplot(data, aes(long, lat, group = group, fill = count)) + 
  geom_polygon() + 
  labs(title = "World map (longlat)") + 
  coord_equal() + 
  labs(fill = "", x = "", y = "") +
  labs(title = paste0("Number of Country Holidays, Terms: \"", i, "\"")) +
  labs(subtitle = "@EvaMaeRey | source: www.timeanddate.com/holidays") +
  theme(legend.position = c(.15, .5), 
        legend.background = element_blank()) +
  theme_opts +
  scale_fill_viridis_c(option = "viridis", direction = 1) 
)
}

```
