# Exports of Medicine

The data plotted for this challenge was simply total export volume of medicine (in dollars).  I played with mapping for this week.  I had fun with trying to create a shadow behind the continents, which I think makes the map look like some kind of a puzzle for children.  I used the wonderful viridis package, which has many good properties for continuous variable plotting.  

```{r}
data <- readxl::read_xlsx("raw_data/Drug & Medicine Exports.xlsx") %>%
  mutate(`Exports (USD millions)` = `Exports (USD)` / 1000000) %>%
  select(-`Exports (USD)`) %>%
  mutate(CountryName = countrycode::countrycode(Exporter, "country.name", "country.name"))
data %>% group_by(Year) %>% tally()

data_wide <- data %>% spread(key = Year, value = `Exports (USD millions)`)

country <- data %>%
  group_by(Exporter) %>%
  summarise(mean_exports = mean(`Exports (USD millions)`, na.rm = T)) %>%
  arrange(desc(mean_exports))

# Mapping data
world_map_df <- map_data("world") %>%
  mutate(CountryName = countrycode::countrycode(region, "country.name", "country.name")) %>%
  filter(region != "Antarctica")

CountriesWorldMap <- world_map_df %>% group_by(CountryName, region) %>% summarise()
data_world_map <- world_map_df %>% full_join(data)

max(data$`Exports (USD millions)`, na.rm = T)
```


```{r, fig.height=12, fig.show="hold"}
# plot map
ggplot() +
  geom_polygon(
    data = data_world_map,
    aes(long - .7, lat - .7, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .6, lat - .6, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .5, lat - .5, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .3, lat - .3, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .4, lat - .4, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .2, lat - .2, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map,
    aes(long - .1, lat - .1, group = group), fill = "grey25"
  ) +
  geom_polygon(
    data = data_world_map %>%
      filter(Year == 2016) %>%
      filter(Exporter != "World"),
    aes(long, lat,
      group = group,
      fill = `Exports (USD millions)`
    )
  ) +
  coord_equal() +
  ggtitle(
    "World of Drug and Medicine Exports",
    "Gina Reynolds @EvaMaeRey | source: www.trademap.org"
  ) +
  scale_fill_viridis_c(
    name = "Exports \n(Millions $US)",
    trans = "log10",
    breaks = c(1, 10, 100, 1000, 10000, 100000)
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(size = 30, family = "Times"),
    plot.subtitle = element_text(size = 18, family = "Times"),
    legend.position = c(.2, .3), legend.text = element_text(size = 12),
    legend.key.size = unit(0.5, "in"),
    legend.background = element_rect(fill = alpha("blue", 0))
  )
```



